Comprehensive Quality-Aware Automated Semantic Web Service Composition

### 2017-04-02 paper.tex
update

\subsection{PSO-based Approach Algorithm}\label{POS-based_algomargin}
The overall algorithm investigated here is made up of a PSO-based web service composition Algorithm \ref{novelSteps} and a decoding Algorithm \ref{graph_building}. In Algorithm \ref{novelSteps}, the  steps $4$, $5$, $6$ and $7$ are different from those of standard PSO: In step 4, the size of task-related service candidates generated by a greedy search determines the size of each particle's position. Each service candidate in a created service candidates queue is mapped to an index of a particle’s position vectors, where each vector has a weight value between 0.0 and 1.0. In step 5, service candidates in the queue are sorted according to their corresponding weight values in descending order. In step 6, this sorted queue is used as one of the inputs of the forward decoding Algorithm \ref{graph_building} to create a $WG$. In step 7, the fitness value of the created $WG$ is the fitness value of the particle calculated by the comprehensive model discussed in \ref{Comprehensive_Quality_Model}.
\vspace{-0.5cm}
\begin{algorithm}
 %\LinesNumbered
 \SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output}
 \SetKwFunction{generateWeightedGraph}{generateWeightedGraph}
 \SetKwProg{Procedure}{Procedure}{}{}
 \SetNlSty{}{}{:}
 Randomly initialise each particle in the swarm\;
  \While {max. iterations not met}{
     \ForEach{particles in the swarm}{
     Create a service candidates queue and map service candidates to a particle's position vectors\;
     Sort the service queue by position vectors' weights\;
     Create a $WG$ from the service queue (Algorithm\ref{graph_building}) \;
     Calculate the $WG$ fitness value\;

>>>>

\subsection{PSO-based Approach Algorithm}\label{POS-based_algomargin}
The overall algorithm investigated here is made up of a PSO-based web service composition technique (Algorithm \ref{novelSteps}) and creating a WG from service queue (Algorithm \ref{graph_building}). In Algorithm \ref{novelSteps}, the  steps $4$, $5$, $6$ and $7$ are different from those of standard PSO: In step 4, the size of task-related service candidates generated by a greedy search determines the size of each particle's position. Each service candidate in a created service candidates queue is mapped to an index of a particle’s position vectors, where each vector has a weight value between 0.0 and 1.0. In step 5, service candidates in the queue are sorted according to their corresponding weight values in descending order. In step 6, this sorted queue is used as one of the inputs of the forward decoding Algorithm \ref{graph_building} to create a $WG$. In step 7, the fitness value of the created $WG$ is the fitness value of the particle calculated by the comprehensive model discussed in \ref{Comprehensive_Quality_Model}.
\vspace{-0.5cm}
\begin{algorithm}
 %\LinesNumbered
 \SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output}
 \SetKwFunction{generateWeightedGraph}{generateWeightedGraph}
 \SetKwProg{Procedure}{Procedure}{}{}
 \SetNlSty{}{}{:}
 Randomly initialise each particle in the swarm\;
  \While {max. iterations not met}{
     \ForEach{particles in the swarm}{
     Create a service candidates queue and map service candidates to a particle's position vectors\;
     Sort the service queue by position vectors' weights\;
     Create a $WG$ from the service queue (Algorithm\ref{graph_building}) \;
     Calculate the $WG$ fitness value\;
